---
title: "Supplementary material"
author: "Marc https://marctang.info"
output:
  html_document:
    df_print: paged
---

For the paper: Tang, Marc and One-Soon Her. 2019. Insights on the Greenberg-Sanches-Slobin Generalization: Quantitative typological data on classifiers and plural markers. Folia Linguistica, 53(2): 297-331.      https://doi.org/10.1515/flin-2019-2013

Load the data and packages
```{r message=FALSE}
set.seed(1)
data<-read.csv("GSSG_ListOfLanguages.csv",sep=";")
#str(plural_data)
library(party)
library(rms)
```

Generate the tree for Figure 2. Conditional inference tree with sortal classifiers as response variable and plural
markers as explanatory variable.
```{r}
tree_Fig2<-ctree(sortal_classifier~morphosyntactic_plural,
                 data=data,
                 controls=ctree_control(testtype = "MonteCarlo",
                                        minbucket=60,mincriterion = 0.99))
plot(tree_Fig2)
```

Calcuate the C index of the tree
```{r}
performance_tree <- unlist(treeresponse(tree_Fig2))[c(FALSE,TRUE)]
somers2(performance_tree,as.numeric(data$sortal_classifier)-1)
```

Generate the tree for figure 3. Conditional inference tree with sortal classifiers as response variable and morpho-
syntactic plural markers, continent, genus as explanatory variables.
```{r}
tree_Fig3<-ctree(sortal_classifier~morphosyntactic_plural + continent + genus,
                 data=data,
                 controls=ctree_control(testtype = "MonteCarlo", 
                                        minbucket=60,mincriterion = 0.99))
plot(tree_Fig3)
```

Calculate the C index of the tree
```{r}
performance_tree <- unlist(treeresponse(tree_Fig3))[c(FALSE,TRUE)]
somers2(performance_tree,as.numeric(data$sortal_classifier)-1)
```

